Online Balanced Graph Partitioning: Optimizations for Large Clusters

### 2020-05-08 paper/disc20clustering.tex
bullet proof cost to OPT

 \title{Tigth Bounds for Online Balanced Graph Partitioning}

@@

\begin{abstract}
	Distributed   applications,  including  batch  processing, streaming, scale-out databases,
	or machine learning, generate a significant amount of network traffic.
	By collocating frequently communicating nodes (e.g., virtual machines) on the same clusters (e.g., server or rack), we can reduce the network load and  improve application performance. 
	However, the communication pattern is a priori unknown and may change over time, hence it needs to be learned in an online manner.
	%
	This paper revisits the online 
	balanced repartitioning problem 
	(introduced by Avin et al.~at DISC 2016)
	which asks for an algorithm that strikes
	an optimal tradeoff between the benefits
	of collocation (i.e., lower network load) 
	and its costs (i.e., migrations). 
	%
	Our first contribution is a significantly improved
	lower bound of $\Omega(k\cdot \ell)$ on the
	competitive ratio, where $\ell$ is the number
	of clusters and $k$ is the cluster size,
	even for a scenario in which the communication
	pattern is static and can be perfectly partitioned;
	we also provide a tight upper bound 
	of $O(k\cdot \ell)$ for this scenario.
	We contribute a tight upper bound
	of $\Theta(\ell)$ for $k=3$,
	for the general model in which the
	communication pattern can change arbitrarily
	over time.
	We improve the result for $k=2$ by providing a strictly $6$-competitive upper bound for the general model.

\end{abstract}

@@

We study a problem of managing the virtual machines in a data center.
We focus on the scenario where virtual machines can be migrated during runtime to another physical machine.
The possibility of migration allows reacting to unpredictable communication patterns.
For example, if some distant virtual machines communicate often, it is vital to reduce their distance to save network bandwidth.
The objective is to~minimize the total network bandwidth used for communication and for migration.

Intuitively, we would like to minimize inter-machine
interactions by mapping frequently communicating virtual machines to the same physical machine
Since communication patterns change over time, the~placement of virtual machines should be managed in an online manner, by migrating them between physical machines.
The~objective is to minimize the weighted sum of inter-machine communication and repartitioning costs.
The former is defined as the number of communication requests between virtual machines placed at distinct physical machines, and the latter as the number of migrations.

@@

We study two models in this paper: a general \emph{partitioning} model, and its subproblem, a \emph{learning} variant.
The general partitioning model was introduced by Avin et al.~\cite{repartition-disc} at DISC 2016.
The learning model was introduced by Henzinger et al.~\cite{sigmetrics19_partitioning} at SIGMETRICS 2019.

\noindent
\textbf{Partitioning model.}
The \emph{balanced repartitioning} problem (\OBRP{})
is a fundamental learning problem
that finds applications in the context of
distributed systems optimization~\cite{repartition-disc}. We are given a set $V$ of $n$ nodes 
(e.g., virtual machines or processes),
initially arbitrarily partitioned into $\ell$~clusters
(e.g., servers or entire racks),
each of size~$k$.
The nodes interact using
a sequence of pairwise communication requests
$\sigma = (u_1,v_1),$ $(u_2,v_2),$ $(u_3,v_3), \ldots$,
where a pair $(u_t,v_t)$ indicates that nodes $u_t$ and $v_t$ exchange a~certain amount of data.
Nodes in $C \subset V$ are \emph{collocated}
if they reside in the same cluster.

@@

\noindent
\textbf{Learning model.}
We study a variant of Online Balanced Partitioning, where communication requests are permanent: once a pair of nodes start communicating, they continue forever.
To avoid infinite cost, each communicating pair must be collocated.
We study instances with finite cost: we assume that the communication graph can be perfectly partitioned in the clusters (no external requests are required).
The algorithm's goal is to \emph{learn} the communication graph, and partition it without too many reconfigurations.
We refer to this problem variant as the \emph{learning} problem.

\medskip 
In both models we assume that the communication patterns are not known in advance to our algorithm.
We measure the~quality of~presented algorithmic solutions by competitive analysis~\cite{borodin-book}, which is well-suited for problems that are online by their nature.
In the competitive analysis, the goal is to~optimize \emph{the competitive ratio} of a given online algorithm: the ratio of its cost to the cost of~an~optimal offline algorithm that knows the whole input sequence in advance.

@@

\maciek{Below is similar to SIDMA, possibly too similar}

The static offline version of~the~partitioning~problem, i.e., a problem variant where
migration is not allowed, where all requests are known in advance, and where
the goal is to find an assignment of $n$ nodes to $\ell$~physical machines, each of~capacity $n/\ell$, is known as the
\emph{$\ell$-balanced graph partitioning problem}. The problem is 
NP-complete, and cannot even be approximated within any finite factor unless P
= NP~\cite{AndRae06}.  The static
variant where $\ell = 2$ corresponds to the minimum bisection problem, which
is already NP-hard~\cite{GaJoSt76}, and 
the currently best approximation ratio is $O(\log n)$~\cite{SarVaz95,ArKaKa99,FeKrNi00,FeiKra02,KraFei06,Raec08}.
The inapproximability of the static variant for general values of $\ell$
motivated research on the bicriteria variant, which can be seen as the offline
counterpart of our capacity augmentation approach. Here, the~goal
is~to~compute a~graph partitioning into $\ell$ components of~size at most~$k$ (where $k > n/\ell$) and the cost of the cut is compared to the optimal (non-augmented)
solution where all components are of a~size at most $n/k$. The variant where
$n \geq 2 \cdot k \cdot \ell$ was considered in
\cite{LeMaTr90,SimTen97,EvNaRS00,EvNaRS99,KrNaSc09}. So far, the~best result~is~an~$O(\!\sqrt{\log n \cdot \log \ell})$-approximation algorithm~\cite{KrNaSc09}.

The studied model is related to online
caching~\cite{SleTar85,FKLMSY91,McGSle91,AcChNo00}, sometimes also referred to
as online caching, where requests for data items (nodes) arrive over time and
need to be served from a cache of finite capacity, and where the number of
cache misses must be minimized. Classic problem variants usually boil down to
finding a smart eviction strategy, such as Least Recently Used (LRU)~\cite{SleTar85}. In our
setting, requests can be served remotely (i.e.,~without fetching the
corresponding nodes to a single physical machine). In this light, our model is more
reminiscent of caching models \emph{with
bypassing}~\cite{EpImLN11,EpImLN15,Irani02}. As a~side result, we show that our problem is
capable of emulating online caching.
A major difference between  these problems is that in the caching problems, each request involves a~single element of the universe, while in our model \emph{both} endpoints of a communication request are subject to~optimization.

@@

\subsection{Our Contributions.}
We provide an improved lower bound 
of $\Omega(k\cdot\ell)$ on the competitive ratio of any online deterministic online algorithm 
even in the learning model;
the best known lower bound so far was $\Omega(k)$,
even for a more general model~\cite{repartition-disc}.
We also present an asymptotically optimal, 
$O(k\cdot \ell)$-competitive algorithm
for the learning model.
For the repartitioning model, we present  
an asymptotically optimal,
$\Theta(\ell)$ algorithm for $k=3$, improving the best known upper bound 
so far $O(\ell^2)$~\cite{repartition-disc}.
Then, we present a strictly $6$-competitive algorithm for $k=2$ that improves upon previous $7$-competitive algorithm with $O(\ell^2)$ additive constant.
%
The overview of known results is in Table~\ref{tab:overview}.

\begin{table*}
	\centering
	\renewcommand{\arraystretch}{1.5}
	\begin{tabular}{>{\centering\arraybackslash}p{4.5cm}|>{\centering\arraybackslash}p{4.5cm}>{\centering\arraybackslash}p{4.5cm}}
		\rowcolor{gray!50}
		\textbf{Variant} & \textbf{ Lower bound} &\textbf{Upper bound}\\ \hline 
		\textbf{$k=2$}& 3\hspace{0.3cm}\cite{repartition-disc} & 6\hspace{0.3cm}(\S \ref{sec:k2}) \\ 
		\rowcolor{gray!25}
		\textbf{$k=3$}&  $\Omega(\ell)$ \hspace{0.3cm}(\S \ref{sec:lowerbound})& $O(\ell) $\hspace{0.3cm}(\S \ref{sec:k3})\\
		$k > 3$ & $\Omega(k\cdot \ell)$\hspace{0.3cm}(\S  \ref{sec:lowerbound})&$O(k^2 \cdot \ell^2)$\hspace{0.1cm} \cite{repartition-disc} \\
		\rowcolor{gray!25}
		Learning model & $\Omega(k\cdot \ell)$\hspace{0.3cm}(\S  \ref{sec:lowerbound})&$O(k \cdot \ell)$\hspace{0.3cm} (\S \ref{sec:ppl}) \\
	\end{tabular}
	\caption{Overview of known results and the results provided in this paper. By $\Rep$ we denote the cost of a single component repartition, and we elaborate on this in Section~\ref{sec:k3}. The results pertain to the general partitioning model, but the last row, that pertains to the learning model for arbitrary $k$ and $\ell$.
	}
	\label{tab:overview}
	\vspace{-7mm}
\end{table*}

@@

\label{alg:PPL}
\begin{algorithm}
	\renewcommand{\algorithmicrequire}{\textbf{Input:}}
	\renewcommand{\algorithmicensure}{\textbf{Output:}}
	\begin{algorithmic}
		%        \Require 
		%        $k, \ell$,
		%        initial configuration $P_I$,
		%        sequence of  requests $\sigma_1, \dots, \sigma_N$ 
		%        \Ensure A final configuration $P_F$ 
		\STATE {For each node $v$ create a singleton component $C_v$ and add it to $\mathcal{C}$}
		\STATE{$P_0 := P_I$}
		\label{line:initcomponents}
		\FOR {each  request $\sigma_t=\{u,v\}, 1 \leq t \leq N$}
		\STATE Let $C_1 \ni u$ and $C_2 \ni v$ be the container components
		\IF{$C_1 \neq C_2$}
		\STATE {Unite the two components into a single component $C'$ and
		$\mathcal{C} = (\mathcal{C}\setminus\set{C_1, C_2}) \cup ~\set{C'}$} \label{line:mergecomponents}
		\IF{$\mathit{cluster}(C_1, P_{t-1}) \neq \mathit{cluster}(C_2, P_{t-1})$
		\COMMENT{i.e.~if not in the same cluster}    
		}       
		\STATE {$P_{t} = \mathit{repartition}(P_{t-1}, P_I, \mathcal{C})$} 
		\COMMENT{move to $P$ closest to $P_I$}
		\label{line:rebalance} 
		\ENDIF
		\ENDIF
		\ENDFOR
	\end{algorithmic}
	\caption{Perfect Partition Learner (\PPL)}
	\label{alg:ppl}
\end{algorithm}

@@

\section{General Partitioning Model}
\label{sec:part}

Now  we discuss the general online
model where the request sequence
can be arbitrary.
In Section~\ref{sec:k3}, we show that the classic \emph{rent-or-buy} approach~\cite{karlin-ski-rental} provides an optimal algorithm for $k=3$.
Then, in Section~\ref{sec:k2}, we show a strictly $6$-competitive algorithm for $k=2$.

\subsection{An Optimal Algorithm for Clusters of Size $3$}
\label{sec:k3}

@@

@@

\subsection{Improved algorithm for Online Rematching}
\label{sec:k2}

@@

	Next,
	we bound  costs incurred by \OPT for requests that trigger collocation of $\{u,v\}$ at $t \in T$.
	If $t$ is the first time that \RM collocates $\{u,v\}$ then  \OPT pays
	$\lambda$ for serving requests in $\sigma_{\set{u,v}}[0,t]$ (remotely),
	or $\alpha$ for collocating the pair and
	serving (some of) the requests with cost 0.
	Therefore in this case,
	$\OPTM (\sigma_{\{u,v\}}(0,t]) \geq  \min{\{ \lambda,\alpha \}}$.
	%
	Otherwise,
	it is not the first collocation and
	consider times $t'$ and $t''$ as define previously,
	 and let 
	$R_t := \sigma_{\{u,w\}}(t'',t'] \cup \sigma_{\{u,v\}}(t',t] $.
	We define $R_{t'}$ for the collocation at $t'$ in an analogous way.
	Then,
	$\OPTM(R_t) = \mathit{OPT} (\sigma_{\{u,w\}}) 
	+ \OPTM(\sigma_{\{u,v\}}) $.
	We distinguish three (non-exhaustive) cases for the cost to \OPT w.r.t.~$R_t$.
	Latter,
	 we argue that \OPT cannot save cost by deviating from these cases.
	\begin{enumerate}[label=\roman*.]
		\item
		\OPT collocates $\{u,w\}$ at  $t''$, $\{u,v\}$  at $t'$,
		and keeps them so during $(t'',t']$ and $(t',t]$, respectively.
		Therefore it serves all requests in $R_t$ with no additional cost and
		let $\OPTM_1 (R_t) := 2\alpha$.
		\item
		\OPT has one of the pairs  already collocated and the other pair separated,
			  prior to and during their respective intervals.
		Hence,
		it pays only $\lambda$ for serving all requests in $R_t$
		and let $\OPTM_2 (R_t) := \lambda$.
		\item
		\OPT has one of the pairs already collocated prior to its interval,
		and it collocates the other pair during the respective interval.
		Then it pays 0 for one pair and $\alpha$ for the other and 
		let $\OPTM_3 (R_t) := \alpha$.
	\end{enumerate}
%	We consider cases (ii) and (iii) also for the pair $\{u,w\}$, symmetrically.
	If \OPT behaves in one of these cases,
	then
	$\mathit{OPT} (R_t) \geq
		\min{\{ \OPTM_1(R_t), \OPTM_2(R_t), \OPTM_3(R_t) \}}  =
		\min{ \{ \lambda, \alpha \}}$.
	Otherwise,
	\OPT deviates from these cases,
	e.g.~by collocating a pair after paying for some of requests to this pair.
	However,
	no deviation can decrease the cost to \OPT. \mahmoud{prove this!}
	Therefore in any case,
	$\mathit{OPT} (R_t) \geq  \min{ \{ \lambda, \alpha \}}$.

	It remains to bound the cost  incurred by \OPT for requests to $\{u,v\}$ that do not lead to its collocation until the end of the sequence at $t=m$.
	If $\{u,v\}$ is not collocated in the initial matching
	and \RM never collocates it,
	then $ C^{m}_{ \{u,v\} } =| \sigma_{\{u,v\}}[1,m] |$.
	\OPT pays
	$\mathit{OPT} (\sigma_{\{u,v\}}[1,m]) 
	\geq \min{ \{ \alpha, C^{m}_{ \{u,v\} } \} }$,
	for collocating this pair or (and) paying for (some of) requests in $\sigma_{\{u,v\}}[1,m]$.
	Else,
	either $\{u,v\}$ is collocated in the initial matching
	or \RM collocates it at some point.
	Then there exists an intersecting pair $\set{u,w}$
	that is collocated by \RM at $t' < m$ (separating $\{u,v\}$).
	We define times $t'' < t' < m$ similarly to the case where \RM collocates $\{u,v\}$.
	Let $R^*_{\{u,v\}} := \sigma_{\{u,w\}} (t'',t'] \cup \sigma_{\{u,v\}} (t',m]$.
	Then,
	we apply cases (i) to (iii) in an analogous way,
	replacing $\lambda$ with $C^{m}_{ \{u,v\}}$ in the analysis.
	Thus, 
	we obtain
	$\mathit{OPT} (R^*_{\{u,v\}}) 
	\geq  \min{ \{ C^{m}_{ \{u,v\}}, \alpha \}}$.

>>>>

 \title{Online Balanced Graph Partitioning: Optimizations for Large Clusters}

@@

\begin{abstract}
	Distributed   applications,  including  batch  processing, streaming, scale-out databases,
	or machine learning, generate a significant amount of network traffic. By collocating frequently communicating nodes (e.g., virtual machines) on the same clusters (e.g., server or rack), the network load can be reduced and application performance improved. 
	However, as the communication pattern is a priori unknown and may change over time, it needs to be learned efficiently, in an online manner.
	%
	This paper revisits the online 
	balanced repartitioning problem 
	(introduced by Avin et al.~at DISC 2016)
	which asks for an algorithm that strikes
	an optimal tradeoff between the benefits
	of collocation (i.e., lower network load) 
	and its costs (i.e., migrations). 
	%
	Our first contribution is a significantly improved
	lower bound of $\Omega(k\cdot \ell)$ on the
	competitive ratio, where $\ell$ is the number
	of clusters and $k$ is the cluster size,
	even for a scenario in which the communication
	pattern is static and can be perfectly partitioned;
	we also provide a tight upper bound 
	of $O(k\cdot \ell)$ for this scenario.
	In addition, we present a tight upper bound
	of $\Theta(\ell)$ for $k=3$,
	for the general model in which the
	communication pattern can change arbitrarily
	over time. 
\end{abstract}

@@

\maciek{Practical motivation}

@@

\maciek{We study two models. One is a subproblem.}

The general model, where $\sigma$ can be arbitrary
was the original problem introduced
by Avin et al.~\cite{repartition-disc} at DISC 2016.
For simplicity, we will refer to the Perfect Partition
model as the \emph{learning} model (as
one has to learn the static communication graph) 
and to the original as the \emph{repartitioning} model (as one continuously adjusts the partition in response to changing communication graph).

\subsubsection{Partitioning model.}
The \emph{balanced repartitioning} problem (\OBRP{})
is a fundamental learning problem
that finds applications in the context of
distributed systems optimization~\cite{repartition-disc}. We are given a set $V$ of $n$ nodes 
(e.g., virtual machines or processes),
initially arbitrarily partitioned into $\ell$~clusters
(e.g., servers or entire racks),
each of size~$k$.
The nodes interact using
a sequence of pairwise communication requests
$\sigma = (u_1,v_1),$ $(u_2,v_2),$ $(u_3,v_3), \ldots$,
where a pair $(u_t,v_t)$ indicates that nodes $u_t$ and $v_t$ exchange a~certain amount of data.
Nodes in $C \subset V$ are \emph{collocated}
if they reside in the same cluster.

@@

\maciek{The competitive ratio definition and the worst case inputs}

\maciek{Ilustrate the challenges. Rent-or-buy. Decision what to evict}

\subsubsection{Learning model.}
In addition to the general model, we study a simplified Perfect Partition model (also studied by Henzinger et al.~\cite{sigmetrics19_partitioning} (SIGMETRICS 2019)) that we consider for a stronger lower bound.
There, we assume that $\sigma$
reveals the edges of a static graph
that can be perfectly partitioned
(no external requests are required).

@@

\maciek{Offline results}
\maciek{Links other problems: for $k=2$ a flavor of online matching, for $\ell = 2$ it generalizes paging}

@@

\subsection{Our Contributions.}
We provide an improved lower bound 
of $\Omega(k\cdot\ell)$ on the competitive ratio of any online deterministic online algorithm 
even in the learning model;
the best known lower bound so far was $\Omega(k)$,
even for a more general model~\cite{repartition-disc}.
We also present an asymptotically optimal, 
$O(k\cdot \ell)$-competitive algorithm
for the learning model.
For the repartitioning model, we present  
an asymptotically optimal,
$\Theta(\ell)$ algorithm for $k=3$;
the best known upper bound 
so far was $O(\ell^2)$~\cite{repartition-disc}.
Then, we present a strictly $6$-competitive algorithm for $k=2$ that improves upon previous $7$-competitive algorithm with $O(\ell^2)$ additive constant..
In addition, we show a new, improved analysis of the algorithm from \cite{repartition-disc} that depends on the solutions to an interesting combinatorial problem (see Section~\ref{ssec:cascade}, The Cascade Problem).
%
The overview of known results is in Table~\ref{tab:overview}.

\begin{table*}
	\centering
	\renewcommand{\arraystretch}{1.5}
	\begin{tabular}{>{\centering\arraybackslash}p{4.5cm}|>{\centering\arraybackslash}p{4.5cm}>{\centering\arraybackslash}p{4.5cm}}
		\rowcolor{gray!50}
		\textbf{Variant} & \textbf{ Lower bound} &\textbf{Upper bound}\\ \hline 
		\textbf{$k=2$}& 3\hspace{0.3cm}\cite{repartition-disc} & 6\hspace{0.3cm}(\S \ref{sec:k2}) \\ 
		\rowcolor{gray!25}
		\textbf{$k=3$}&  $\Omega(\ell)$ \hspace{0.3cm}(\S \ref{sec:lowerbound})& $O(\ell) $\hspace{0.3cm}(\S \ref{sec:k3})\\
		$k > 3$ & $\Omega(k\cdot \ell)$\hspace{0.3cm}(\S  \ref{sec:lowerbound})&$O(k \cdot \ell \cdot \min \{ k \cdot \ell, \Rep(k, \ell) \})$\hspace{0.1cm} (\S \ref{sec:k3}) \\
		\rowcolor{gray!25}
		Learning model & $\Omega(k\cdot \ell)$\hspace{0.3cm}(\S  \ref{sec:lowerbound})&$O(k \cdot \ell)$\hspace{0.3cm} (\S \ref{sec:ppl}) \\
	\end{tabular}
	\caption{Overview of known results and the results provided in this paper. By $\Rep$ we denote the cost of a single component repartition, and we elaborate on this in Section~\ref{sec:k3}. The results pertain to the general partitioning model, but the last row, that pertains to the learning model for arbitrary $k$ and $\ell$.
	}
	\label{tab:overview}
	\vspace{-7mm}
\end{table*}

@@

\section{PPL Algorithm} \label{alg:PPL}
\begin{algorithm}
	\renewcommand{\algorithmicrequire}{\textbf{Input:}}
	\renewcommand{\algorithmicensure}{\textbf{Output:}}
	\begin{algorithmic}
		%        \Require 
		%        $k, \ell$,
		%        initial configuration $P_I$,
		%        sequence of  requests $\sigma_1, \dots, \sigma_N$ 
		%        \Ensure A final configuration $P_F$ 
		\STATE {For each node $v$ create a singleton component $C_v$ and add it to $\mathcal{C}$}
		\STATE{$P_0 := P_I$}
		\label{line:initcomponents}
		\FOR {each  request $\sigma_t=\{u,v\}, 1 \leq t \leq N$}
		\STATE Let $C_1 \ni u$ and $C_2 \ni v$ be the container components
		\IF{$C_1 \neq C_2$}
		\STATE {Unite the two components into a single component $C'$ and
		$\mathcal{C} = (\mathcal{C}\setminus\set{C_1, C_2}) \cup ~\set{C'}$} \label{line:mergecomponents}
		\IF{$\mathit{cluster}(C_1, P_{t-1}) \neq \mathit{cluster}(C_2, P_{t-1})$
		\COMMENT{i.e.~if not in the same cluster}    
		}       
		\STATE {$P_{t} = \mathit{repartition}(P_{t-1}, P_I, \mathcal{C})$} 
		\COMMENT{move to $P$ closest to $P_I$}
		\label{line:rebalance} 
		\ENDIF
		\ENDIF
		\ENDFOR
	\end{algorithmic}
	\caption{Perfect Partition Learner (\PPL)}
	\label{alg:ppl}
\end{algorithm}

@@

\section{The Partitioning Problem}
\label{sec:part}

@@

\subsection{Improved analysis of the component-based algorithm}
\label{sec:k3}

@@

\subsection{Warm-up: bounding the reconfiguration for $k=3$}

Corollary: DET2 is $O(\ell)$-competitive for $k=3$.

\section{Improved algorithm for Online Rematching}
\label{sec:k2}

@@

	Next,
	we bound  costs incurred by \OPT for requests that trigger collocation of $\{u,v\}$ at $t \in T$.
	If $t$ is the first time that \RM collocates $\{u,v\}$ then  \OPT pays
	$\lambda$ for serving requests in $\sigma_{\set{u,v}}[0,t]$ (remotely),
	or $\alpha$ for collocating the pair and
	serving (some of) the requests with  cost zero.
	Therefore in this case,
	$\OPTM (\sigma_{\{u,v\}}(0,t]) \geq  \min{\{ \lambda,\alpha \}}$.
	%
	Otherwise,
	it is not the first collocation and
	consider times $t'$ and $t''$ as define previously,
	 and let 
	$R_t := \sigma_{\{u,w\}}(t'',t'] \cup \sigma_{\{u,v\}}(t',t] $.
	We define $R_{t'}$ for the collocation at $t'$  analogously.
	Then,
	$\OPTM(R_t) = \mathit{OPT} (\sigma_{\{u,w\}}) 
	+ \OPTM(\sigma_{\{u,v\}}) $.
	Note that \OPT cannot have both pairs collocated at the same time.
	However, it can have one of the pairs already collocated prior to its respective interval.
	Let us assume  \OPT has one pair,
	e.g.~$\{u,v\}$ collocated already prior its respective interval, i.e.~$(t',t]$,
	 and keeps it so during the interval.
	 Then it pays zero while serving $\sigma_{\{u,v\}}$.
	Hence,
	it must pay $\alpha$ for collocating the other pair, in this case $\{u,w\}$,
	or (resp., and) it pays (resp., up to) $\lambda$ for serving (resp., some of) requests in $\sigma_{\{u,w\}}$. 
	Therefore in any case $\OPTM(R_t) \geq  \min{\{ \lambda,\alpha \}}$.
	\begin{comment}
	We distinguish three (non-exhaustive) cases for the cost to \OPT w.r.t.~$R_t$.
	Latter,
	 we argue that \OPT cannot save cost by deviating from these cases.
	\begin{enumerate}[label=\roman*.]
		\item
		\OPT collocates $\{u,w\}$ at  $t''$, $\{u,v\}$  at $t'$,
		and keeps them so during $(t'',t']$ and $(t',t]$, respectively.
		Therefore it serves all requests in $R_t$ with no additional cost and
		let $\OPTM_1 (R_t) := 2\alpha$.
		\item
		\OPT has one of the pairs  already collocated and the other pair separated,
			  prior to and during their respective intervals.
		Hence,
		it pays only $\lambda$ for serving all requests in $R_t$
		and let $\OPTM_2 (R_t) := \lambda$.
		\item
		\OPT has one of the pairs already collocated prior to its interval,
		and it collocates the other pair during the respective interval.
		Then it pays 0 for one pair and $\alpha$ for the other and 
		let $\OPTM_3 (R_t) := \alpha$.
	\end{enumerate}
%	We consider cases (ii) and (iii) also for the pair $\{u,w\}$, symmetrically.
	If \OPT behaves in one of these cases,
	then
	$\mathit{OPT} (R_t) \geq
		\min{\{ \OPTM_1(R_t), \OPTM_2(R_t), \OPTM_3(R_t) \}}  =
		\min{ \{ \lambda, \alpha \}}$.
	Otherwise,
	\OPT deviates from these cases,
	e.g.~by collocating a pair after paying for some of requests to this pair.
	However,
	no deviation can decrease the cost to \OPT. \mahmoud{prove this!}
	Therefore in any case,
	$\mathit{OPT} (R_t) \geq  \min{ \{ \lambda, \alpha \}}$.
	\end{comment}

	It remains to bound the cost  incurred by \OPT due to requests to $\{u,v\}$ that do not lead to its collocation until the end of the sequence at $t=m$.
	We bound the cost analogously to the case where \RM collocates $\{u,v\}$.
	If $\{u,v\}$ is not collocated in the initial matching
	and \RM never collocates it,
	then $ C^{m}_{ \{u,v\} } =| \sigma_{\{u,v\}}[1,m] |$.
	\OPT pays
	$\mathit{OPT} (\sigma_{\{u,v\}}[1,m]) 
	\geq \min{ \{ \alpha, C^{m}_{ \{u,v\} } \} }$,
	for collocating this pair or (and) paying for (resp.~some of) requests in $\sigma_{\{u,v\}}[1,m]$.
	Else,
	either $\{u,v\}$ is collocated in the initial matching
	or \RM collocates it at some point.
	Then there exists an intersecting pair $\set{u,w}$
	that is collocated by \RM at $t' < m$ (separating $\{u,v\}$).
	We define times $t'' < t' < m$ similarly as in the former case.
	Let $R^*_{\{u,v\}} := \sigma_{\{u,w\}} (t'',t'] \cup \sigma_{\{u,v\}} (t',m]$.
	Then,
	\OPT must pay for collocating at least one pair or (and) serving requests 
	to the other pair remotely.
	Thus,
	$\mathit{OPT} (R^*_{\{u,v\}}) 
	\geq  \min{ \{ C^{m}_{ \{u,v\}}, \alpha \}}$.
